### 2013-05-09 doc/icml2013/discussion.tex
finish experiments

In this paper, we take a first step at developing computationally efficient and
statistically consistent estimators for discriminative latent-variable models
by focusing on mixture of linear regressions. We showed that by regressing on
higher-order powers of the data with a regularizer that encourages low rank
structure, coupled with an efficient tensor power method, we obtain a very natural algorithm.
Empirically, our algorithm can outperform EM, and when used to initialize EM,
yields significantly more accurate and stable results.

>>>>

In this paper, we developed a computationally efficient and statistically
consistent estimator for mixture of linear regressions.
Our algorithm, Spectral
Experts, regresses on higher-order powers of the data with a regularizer that
encourages low rank structure, followed by tensor factorization to recover the
actual parameters.  Empirically, we found Spectral Experts 
to be an excellent initializer for EM.
%yielding significantly more accurate and stable results than EM.
